### 2024-08-08 getting-started.qmd
20240808 - minimal reproducible example

- Read the posting guidelines before posting!
- Be respectful of other people and their time.
`R` is free software.
People are offering their free time to help.
They are under no obligation to help you.
If you are disrespectful or act like they owe you anything, you will rub people the wrong way and will be less likely to get help.
- Provide a minimal, reproducible example.
Providing a minimal, reproducible example can be crucial for getting a helpful response.
By going to the trouble of creating a minimal reproducible example and identifying the minimum conditions necessary to reproduce the issue, you will often figure out how to resolve it.
Here are guidelines on providing a minimal reproducible example: <https://stackoverflow.com/help/minimal-reproducible-example> (archived at <https://perma.cc/6NUB-UTYF>).
My strong recommendation is to provide a `reprex` whenever possible: <https://reprex.tidyverse.org>.

>>>>

- Read the posting guidelines before posting!
- Be respectful of other people and their time.
`R` is free software.
People are offering their free time to help.
They are under no obligation to help you.
If you are disrespectful or act like they owe you anything, you will rub people the wrong way and will be less likely to get help.
- Provide a minimal, reproducible example.
Providing a minimal, reproducible example can be crucial for getting a helpful response.
By going to the trouble of creating a minimal, reproducible example and identifying the minimum conditions necessary to reproduce the issue, you will often figure out how to resolve it.
Here are guidelines on providing a minimal, reproducible example: <https://stackoverflow.com/help/minimal-reproducible-example> (archived at <https://perma.cc/6NUB-UTYF>).
Here are a good example and guidelines for providing a minimal, reproducible example in `R`: <https://stackoverflow.com/a/5963610> (archived at <https://perma.cc/PC9L-DQZG>).
My strong recommendation is to provide a `reprex` whenever possible: <https://reprex.tidyverse.org>.
